Mathematical Aspects of the Capital Market

### 2014-05-08 thesis/thesis.tex
Add the additions of stock case studies.

\chapter{Summary of the Results}
The results of this thesis project are the following:
\begin{enumerate}
\item ARIMA log-volatility model
  \begin{enumerate}
  \item ARIMA log-volatility returns' models are justified and tested
    against Nordea Bank 15-minute returns and Volvo B 30-minute returns
    during the period 2013/10/10 - 2014/04/04. Historical volatility's
    are estimated using ``realized volatilities'', denoted
    $\hat{\sigma}_t$ here:
    \begin{eqnarray*}
      \hat{\sigma}_t &=& \sqrt{
        \sum_{i = 1}^n \left[\ln {p_{t - \Delta t + i \Delta t / n} \over
            p_{t - \Delta t + (i-1) \Delta t / n}} \right]^2
      }
    \end{eqnarray*}
    where $p_{t'}$ is the price of the asset at time $t'$, and $n$ is
    the number of sub intervals into which the time interval $[t -
    \Delta t, t]$ is divided. A discussion of the choice of $n$ is found
    in \S\ref{sec:SLV_model}.

    Using the first 80\% of the data for estimating the model and the
    last 20\% for comparing with the model forecast, we find the ARIMA
    models out-perform their GARCH competitors in most cases.

  \item The unconditional distribution functions of ARIMA
    log-volatility models are calculated (equation
    \ref{eq:UncondPDFAsymmetric} and \ref{eq:UncondPDFAsymmetric1}):
    The unconditional distribution of  the returns $r_t$ is the same as
    $\mu + e^{\bar{v} + \sigma a} b$, where $(a, b) \sim N(0, \Sigma)$
    \begin{eqnarray*}
      \Sigma &=&
      \begin{pmatrix}
        1 & \psi \\
        \psi & 1
      \end{pmatrix}
    \end{eqnarray*}
    Then the PDF of the unconditional distribution $f_r(x)$ can be expressed as
    \begin{eqnarray*}
      f_{r'}(x) &=& {1 \over 2\pi \sqrt{1 - \psi^2}} \times \\
      && \int_{-\infty}^\infty da \exp
      \left[- {
          a^2 + 2\sigma(1 - \psi^2)a - 2a\psi e^{-a\sigma} x + e^{-2a\sigma} x^2
          \over
          2(1 - \psi^2)
        }
      \right] \\
      f_r(x) &=&  \td{r'}{r} f_{r'}[e^{-\bar{v}} (x - \mu)] \\
      &=& e^{-\bar{v}} f_{r'}[e^{-\bar{v}} (x-\mu)] \\
    \end{eqnarray*}
    where $r' = e^{\sigma a}b$. The moment generating function of the
    unconditional distribution is found as an integral, and all the
    moments can be evaluated in closed form. See equations
    \ref{eq:AsymmetricMoments}.

  \end{enumerate}
\item Correlation matrix of Gaussian returns. $N$ series of
  auto-correlated, standard Gaussian distributed returns are simulated
  to form $N\times N$ correlation matrix $C$:
  \begin{eqnarray*}
    r_{it} &=& \phi r_{i,t-1} + a_t \\
    C_{ij} &=& {1 \over T} \sum_{t=1}^T r_{it} r_{jt}
  \end{eqnarray*}
  where $i = 1, 2, ..., N$ and $t = 1,2, ..., T$. $a_t \sim N(0,
  1)$.
  \begin{enumerate}
  \item Distribution of the elements of C. The asymptotic distribution
    of the matrix elements $C_{ii}$ and $C_{ij}$ ($i \neq j$) are 
    Gaussian whose mean and variance are functions of $\phi$:
    \begin{eqnarray*}
      \E(C_{ij}) &=& {\sigma^2 \over \sqrt{2\pi} (1 - \phi^2)(1 -
        \rho^2)^{1/4}} \left[ P^{-3/2}_{-1/2}(-\rho) -
        P^{-3/2}_{-1/2}(\rho)
      \right] \\
      \var(C_{ij}) &=& {2 \sigma^6 \over T (1 - \phi^2)^2} \left[
        {\phi^2 \over 1 - \phi^2} -
        {\phi^2 (1 - \phi^{2T}) \over
          T(1 - \phi^2)}
      \right] + {\sigma^4 (1 - \rho^2)^2 v^2(\rho) \over
        T (1 - \phi^2)^2} \\
      &\approx& {2 \sigma^6 \phi^2 \over T (1 - \phi^2)^3}
      + {\sigma^4 (1 - \rho^2)^2 v^2(\rho) \over
        T (1 - \phi^2)^2}
    \end{eqnarray*}
    where $\rho = \text{corr}(a_{it}, a_{jt})$, $i \neq
    j$. $P^\mu_\nu(\cdot)$ is Ferrers function of the first kind (See
    equation \ref{eq:Ferrers_1st}) and
    \begin{eqnarray*}
      v^2(\rho) &=&
      {4 \over \sqrt{2\pi} (1 - \rho^2)^{7/4}} \left[
        P^{-5/2}_{-1/2}(\rho) + P^{-5/2}_{-1/2}(-\rho)
      \right] \\
      && - {1 \over 2\pi (1 - \rho^2)^{5/2}} \left[
        P^{-3/2}_{-1/2}(-\rho) - P^{-3/2}_{-1/2}(\rho)
      \right]^2
    \end{eqnarray*}
    In comparison,
    \begin{eqnarray*}
      \E(C_{ii}) & \approx & {\sigma^2 \over 1 - \phi_1^2} \left[
        1 - {\phi_1^2 \over T}
      \right] \\
      \var(C_{ii}) &\approx& {2 \sigma^4 \over T (1 - \phi_1^4)} +
      {\sigma^6 \over T (1 -\phi_1^2)^2}
    \end{eqnarray*}

  \item Distribution of the maximum eigenvalue of C. It is shown that
    the maximum eigenvalue has approximately a gamma distribution even
    when auto-correlations are present among the returns. The mean of
    the gamma distribution is approximately quadratic in $\tan{\pi\phi
      \over 2}$.
  \end{enumerate}

\item Covariance matrix C of GARCH(1,1) processes. In the limit of
  very long return series, the covariance matrix of properly
  specified GARCH(1,1) processes (see chapter
  \ref{chp:CrossCorrelationFat}) is 
  shown to be diagonal. The distribution of its eigenvalues thus
  coincides with that of its diagonal elements. Their distribution
  converges to an $\alpha$-stable distribution. If the returns $r_{it}$
  have tail behavior $P(|r_{it}| > x) \sim {c \over x^\alpha}$, the
  asymptotic stable distribution has L\'evy index
  $\alpha/2$. Moreover, the mean of this stable distribution scales
  with the length of the return series (T) as $T^{1 - 2/\alpha}$,
  while the width is independent of T.

  In contrast, the distribution of the non-diagonal elements of the
  covariance matrix converges to a symmetric, zero-centered, stable
  distribution with a different L\'evy index than $\alpha$. Denote it
  $\alpha'$, then the variance of this stable distribution scales with
  T as $T^{1/\alpha' - 2/\alpha}$.

  When the return series only have a modest length, the situation is
  studied in terms of the localization of the eigenvectors. For a
  given T, the largest eigenvalues correspond to the most localized
  eigenvectors, and the extent of localization decreases as the
  eigenvalue decreases. As T increases, the extent of localization
  increases for all eigenvectors.

  Auto-correlations among the returns, on the other hand, reduces the
  extent of localization, and also the certainty of localization with
  respect to the eigenvalues. In other words, if the return series
  have considerable auto-correlations, the eigenvectors corresponding
  to the largest eigenvalues will have a rather fractured composition.
\end{enumerate}

\chapter{Appendix}
\section{PDF of the covariance matrix of auto-correlated Gaussian
  Returns} \label{app:pdf_gaussian1}
When autocorrelations exist among the columns of the Gaussian returns
matrix $\mtx R$, the distribution of the covariance matrix $\mtx C =
\mtx{R} \mtx{R'}$ is no longer Wishart but is nonethelss closely
related to it. In the following we consider the situation where
$r_{i,t}$ can be represented as a vector auto-regressive
process. Specifically, suppose
\begin{eqnarray*}
  \vec{r}_t &=& \sum_{k=1}^p \phi_k \vec{r}_{t-k} + \vec{a}_t \\
  \vec{a}_t &=& \vec{r}_t - \sum_{k=1}^p \phi_k \vec{r}_{t-k}
\end{eqnarray*}
where $\vec{a}_t = (a_{1,t}, a_{2,t}, \cdots, a_{N,t})' \sim N(0,
\Sigma)$ and comprise the columes of $\mtx A$; $\vec{r}_t$ are the
columes of $\mtx R$. Here $N(0, \Sigma)$ denotes the multivarate
normal distribution with covariance matrix $\Sigma$. The last equation
can be written in matrix form
\[
A = R M
\]
For example, in the case of an AR(1) process
\begin{equation*}
  \begin{pmatrix}
    a_{1,1} & a_{1,2} & \cdots & a_{1,T} \\
    \vdots & \ddots & \vdots \\
    a_{N,1} & a_{N,2} & \cdots & a_{N,T} \\
  \end{pmatrix} =
  \begin{pmatrix}
    r_{1,1} & r_{1,2} & \cdots & r_{1,T} \\
    \vdots & \ddots & \vdots \\
    r_{N,1} & r_{N,2} & \cdots & r_{N,T} \\
  \end{pmatrix}
  \begin{pmatrix}
    1 & -\phi_1 &   &   & \\
      & 1 & -\phi_1 &   & \\
      &   & \ddots  & \ddots &   \\
      &   &   & 1 & -\phi_1 \\
      &   &   &   & 1 \\
  \end{pmatrix}
\end{equation*}
Let $QR = RM$, then $Q = RMR^{-1}$. Since the set of $\{r_{ij}\}$ for
which $\text{det } R = 0$ has probability zero, a matrix $Q$
satisfying the above equation almost surely exists. Thus $A = RM =
QR$ and $AA' = QRR'Q'$ Since the columns of A are not auto-correlated,
$AA' \sim W(\Sigma, T)$. Then $RR' \sim W(Q^{-1} \Sigma Q'^{-1}, T)$
follows from \cite{Anderson2003}, \S7.3.3.

Now we observe that $\Sigma$ enters $f(RR')$ through $\tr (\Sigma^{-1}
RR')$ and $\det \Sigma$. $RR'$ enters through $\tr (\Sigma^{-1}
RR')$ and $\det (RR')$. Clearly
\begin{eqnarray*}
  \det (Q^{-1}\Sigma Q'^{-1}) &=& \det \Sigma \over (\det Q)^2 \\
  &=& \det \Sigma \over (\det M)^2 \\
  &=& \det \Sigma
\end{eqnarray*}
As to $\tr (\Sigma^{-1} C)$, we have
\begin{eqnarray*}
  && \tr\left[(Q^{-1}\Sigma Q'^{-1})^{-1} RR'\right] \\
  &=& \tr\left[Q'\Sigma^{-1} Q RR'\right] \\
  &=& \tr\left[ R'^{-1}M'R'\Sigma^{-1} RMR^{-1} RR'\right] \\
  &=& \tr\left[ \Sigma^{-1} RM (RM)'\right] \\
  &=& \tr\left[ \Sigma^{-1} AA'\right] \\
\end{eqnarray*}

Moreover, $\det RR' = \det AM^{-1} M'^{-1} A' = \det AA'$.

Thus if we use $f_R(\cdot)$ to denote the joint probability density of
the entries of RR' and $f_A(\cdot)$ to denote that of AA', we can
write
\begin{equation}\label{eq:cross-corr-matrix-PDF}
  f_R(RR') = f_A(RMM'R')
\end{equation}

Substituting for $f_A$ the Wishart probability density function (PDF)
\ref{eq:WishartPDF}, we get the PDF of $RR'$.

\section{Eigenvalue distribution of Wishart Matrix}
\label{sec:wishart_eigen_dist}
In this section we summarize the analytic results regarding the
eigenvalue distribution of a Wishart matrix $\mtx{RR'}$. In the
simplest case where the elements of $\mtx R$ are all independent of
each other, i.e. neither auto-correlation nor cross-correlation
exists, we have \cite{Chiani2012}
\begin{eqnarray}
  f_{\lambda}(x_1, \cdots, x_N) &=& K \prod_{i=1}^N e^{-x_i/2}
  x_i^{(T-N-1)/2} \prod_{i<j}^N (x_i -
  x_j) \label{eq:wishart_eigen_pdf}\\
\end{eqnarray}
where the eigenvalues have been indexed in descending order: $x_1 \geq
x_2 \geq \cdots \geq x_N$. The normalization constant K is given by
\begin{equation*}
  K = {\pi^{N^2/2} \over 2^{NT/2}\Gamma_N(T/2) \Gamma_N(N/2)}
\end{equation*}
where the function $\Gamma_m(a)$ is defined as
\begin{equation*}
  \Gamma_m(a) = \pi^{m(m-1)/4} \prod_{k=1}^m \Gamma\left(a - {k-1
      \over 2}\right)
\end{equation*}
Moreover, K. Johnsson \cite{Johnsson2000} and I. Johnstone
\cite{Johnstone2001} showed that, at the {\it absence} of
autocorrelations and in the asymptotic limit $N, T \to \infty$, $N/T
\to q < \infty$, the maximum eigenvalue  $\lambda_1$ follows the
Tracy-Widom distribution (denote $\mathscr{TW}_1$ here) when properly
relocated and rescaled:
\begin{equation*}
  {\lambda_1 - \mu_{NT} \over \sigma_{NT}} \sim \mathscr{TW}_1
\end{equation*}
where $\mu_{NT}$ and $\sigma_{NT}$ are given by
\begin{eqnarray*}
  \mu_{NT} &=& \left(
    \sqrt{N-1/2} + \sqrt{T - 1/2}
  \right)^2 \\
  \sigma_{NT} &=& \sqrt{\mu_{NT}} \left(
    {1 \over \sqrt{N-1/2}} + {1 \over \sqrt{T-1/2}}
  \right)^{1/3}
\end{eqnarray*}
The $\mathscr{TW}_1$ distribution has the following cummulative
distribution function (CDF) \cite{Chiani2012}
\begin{equation*}
  F_1(x) = \exp\left[
    -{1 \over 2} \int_x^\infty dy \left(q(y) + (y-x)q^2(y)\right)
  \right]
\end{equation*}
where $q(y)$ is defined as the solution to the Painlev\'e II differential
equation
\begin{equation*}
  q''(y) = yq(y) + 2q^3(y)
\end{equation*}
which is unique when imposing the condition
\begin{equation*}
  q(y) \sim \text{Ai}(y) \text{ as } y \to \infty
\end{equation*}

Then Marco Chiani showed recently that the $\mathscr{TW}_1$ distribution
can be well approximated by a gamma distribution based on his proof
that the exact distribution of the maximum eigenvalue is a mixture of
gamma distributions. Specifically,
\begin{equation}\label{eq:TracyWidom-Gamma}
  {\lambda_1 - \mu_{NT} \over \sigma_{NT}} + \alpha \sim
  \mathscr{G}(k ,\theta)
\end{equation}
where $\mathscr{G}(k, \theta)$ denotes the Gamma distribution with
parameters $k$ and $\theta$ \cite{Chiani2012}. The probability
density function (PDF) of the gamma distribution is given by
\begin{equation*}
  f_\gamma(x; k, \theta) = {1 \over \Gamma(k) \theta^k} x^{k-1}
  e^{-x/\theta}
\end{equation*}
Moreover, the first 3 moments of the distribution are simple:
\begin{eqnarray*}
  \text{mean} &=& k\theta \\
  \text{variance} &=& k\theta^2 \\
  \text{skewness} &=& 2/\sqrt{k}
\end{eqnarray*}

\section{Collection of Figures and Tables}
\begin{figure}[htb!]
  \centering
  \subfigure[ACF of $z_t$]{
    \includegraphics[scale=0.4, clip=true, trim=95 236 118
    200]{../pics/nordea_15min_quotient_acf.pdf}
    \label{fig:nordea_15min_quotient_acf}
  }
  \subfigure[ACF of $z_t^2$]{
    \includegraphics[scale=0.4, clip=true, trim=95 236 118
    200]{../pics/nordea_15min_quotient_squared_acf.pdf}
    \label{fig:nordea_15min_quotient_squared_acf}
  }
  \caption{\small \it Nordea 15min $z_t$ and $z_t^2$ auto-correlation
    function (ACF).}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfigure[Normal Probability Plot of $y_t$]{
    \includegraphics[scale=0.4, clip=true, trim=76 256 109
    214]{../pics/nordea2_y_normplot.pdf}
    \label{fig:nordea_15min_y_qq}
  }
  \subfigure[ACF of $y_t$]{
    \includegraphics[scale=0.4, clip=true, trim=92 258 104
    218]{../pics/nordea_15min_y_acf.pdf}
    \label{fig:nordea_15min_y_acf}
  }
  \caption{\small \it Nordea 15min $y_t$ normal probability plot and
    autocorrelations}
\end{figure}

\begin{figure}[htb!]
  \begin{center}
    \includegraphics[scale=0.4, clip=true, trim=90 228 115
    226]{../pics/GaussianMarkovSpectrumPDF.pdf}
  \end{center}
  \vspace{-10mm}
  \caption{\small \it
      Eigenvalue distribution with $\tau$ ranging from 0 to
      3. The 1st blue line, which is shown as stairs, is the
      theoretical eigenvalue distribution according to the
      Marcenko-Pastur law: $f(\lambda) = \sqrt{(\lambda_+/\lambda - 1)(1
        - \lambda/\lambda_-)}/2\pi q \sigma^2$, where $\lambda_{\pm} =
      \sigma^2(1 \pm \sqrt{q})^2$ In the simulation we have
      chosen $q = N/T = 50/1000 = 0.05$ and $\sigma=1$. For each value
      of $\tau$ we generate 2000 instances of $N \times T$ random matrix
      $R$, and compute C as $C=RR'/T$. Hence each curve in the figure is
      constructed from 2000 sets of eigenvalues.
    }
  \label{fig:GaussianMarkovSpectrumPDF}
\end{figure}

\begin{figure}[htb!]
  \centering
  \includegraphics[scale=0.4, clip=true, trim=100 226 116
  133]{../pics/Gaussian_mineig.pdf}
  \caption{\small \it The minimum eigenvalue versus
    auto-correlation strength $\phi$. For each value of $\phi$ 2000
    random matrices are generated and their eigenvalues are
    calculated. The minimum eigenvalue of each random matrix is noted
    and the mean of the 2000 such minimum eigenvalues are plotted
    against the chosen value of $\phi$. 20 values of $\phi$ are
    included in the plot, ranging from 0 to 0.95 with step size 0.05.}
  \label{fig:Gaussian_mineig}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[scale=0.5, clip=true, trim=0 238 0
    197]{../pics/GaussianMarkov005MaxEigCDF_loglog.pdf}
  \end{center}
  \caption{\small \it Cummulative distribution function (CDF) of the maximum
    eigenvalue ($\lambda_1$). Blue: empirical CDF. Red: CDF of the
    fitting gamma distribution. Each pair of CDFs correspond to a
    fixed autocorrelation strength ($\phi$). The parameters $k$ and
    $\theta$ of the gamma distribution are fit to data by matching the
    2nd and the 3rd moments of the gamma distribution to the
    corresponding moments of the empirical distribution. Then the
    parameter $\alpha$ in equation \ref{eq:TracyWidom-Gamma} is chosen
    to be $\alpha = k\theta - \E\left({\lambda_1 - \mu_{NT} \over
        \sigma_{NT}}\right)$. The curves are plotted on log-log
    scale.}
  \label{fig:GaussianMarkov005MaxEigCDF_loglog}
  %\vspace{-10mm}
\end{figure}

\begin{figure}[htb!]
  \centering
  \includegraphics[scale=0.5, clip=true, trim=50 233 63
  136]{../pics/Volvo_B_30m_returns.pdf}
  \caption{\small \it Volvo B 30min returns' unconditional distribution fit to
    the Stochastic Volatility model. The time series runs from
    2013/10/10 to 2014/03/12. Left: $P(r < x)$ with $x < 0$; Right:
    $P(r > x)$ with $x > 0$. Both plots are on log-log scale.}
  \label{fig:Volvo_B_30m_returns}
\end{figure}

\begin{figure}[htb!]
  \centering
  \includegraphics[scale=0.5, clip=true, trim=65 241 72
  143]{../pics/Nordea_30m_returns.pdf}
  \caption{\small \it Nordea Bank 30min returns' unconditional
    distribution fit to the Stochastic Volatility model. The time
    series runs from 2013/10/10 to 2014/03/12. Left: $P(r < x)$ with
    $x < 0$; Right: $P(r > x)$ with $x > 0$. Both plots are on log-log scale.}
  \label{fig:Nordea_30m_returns}
\end{figure}

\begin{figure}[htb!]
  \centering
  \includegraphics[scale=0.5, clip=true, trim=21 241 28
  146]{../pics/Ericsson_30m_returns.pdf}
  \caption{\small \it Ericsson B 30min returns' unconditional
    distribution fit to the Stochastic Volatility model. The time
    series runs from 2013/10/10 to 2014/03/12. Left: $P(r < x)$ with
    $x < 0$; Right: $P(r > x)$ with $x > 0$. Both plots are on log-log scale.}
  \label{fig:Ericsson_30m_returns}
\end{figure}

\begin{figure}[htb!]
  \centering
  \includegraphics[scale=0.5, clip=true, trim=0 197 0
  154]{../pics/garch_eigenvec_Cmax_corr.pdf}
  \caption{\small \it Eigenvectors' largest component in
    correspondence to the eigenvalues. N is fixed to 50.}
  \label{fig:garch_eigenvec_Cmax_corr}
\end{figure}

\begin{figure}[htb!]
  \centering
  \includegraphics[scale=0.5, clip=true, trim=85 258 103
  229]{../pics/GarchSpectrumAutocorrelated.pdf}
  \caption{\small \it Eigenvalue distribution of cross-correlation
    matrix built from auto-correlated GARCH processes. $\phi$ = 0,
    0.5, 0.8, 0.955, 0.97 correspond to correlation time $\tau$ =
    0, 1.00, 3.11, 15.05, 22.76.}
  \label{fig:GarchSpectrumAutocorrelated}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfigure[]{
    \includegraphics[scale=0.4, clip=true, trim=95 260 111
    232]{../pics/garch_eigenvec_PR_dist_corr.pdf}
    \label{fig:garch_eigenvec_PR_dist_corr}
  }
  \subfigure[]{
    \includegraphics[scale=0.4, clip=true, trim=95 260 111
    232]{../pics/garch_eigenvec_Cmax_dist_corr.pdf}
    \label{fig:garch_eigenvec_Cmax_dist_corr}
  }
  \caption{\small \it \ref{fig:garch_eigenvec_PR_dist_corr}: PDF of
    the normalized participation ratio
    (PR). \ref{fig:garch_eigenvec_Cmax_dist_corr}: PDF of the largest
    component of the eigenvectors. N is fixed to 50. $\phi$ values of
    0, 0.6000, 0.9000, 0.9900 correspond to correlation time $\tau$ =
    0, 1.3569, 6.5788, 68.9676}
\end{figure}

\begin{figure}[htb!]
  \centering
  \subfigure[]{
    \includegraphics[scale=0.38, clip=true, trim=93 229 115
    134]{../pics/localization_ratio.pdf}
    \label{fig:localization_ratio}
  }
  \subfigure[]{
    \includegraphics[scale=0.38, clip=true, trim=87 227 115
    133]{../pics/localization_ratio2.pdf}
    \label{fig:localization_ratio2}
  }
  \caption{\small \it \ref{fig:localization_ratio}: Ratio of localized
    eigenvectors versus the auto-correlation strength $\phi$. Black
    ``+'': ratio of localized eigenvectors as measured by the number
    of participating basis vectors being lower than 2; Black ``x'':
    ratio of localized eigenvectors as measured by the largest
    component being larger than 0.9. Blue curve: quadradic function
    fitted to ``+''. Green curve: quadratic function fitted to
    ``x''. There are 27 data points in the plot, corresponding to 27
    $\phi$ values: 0 to 0.8 with step size 0.05, and 0.9 to 0.99 with
    step size 0.01. The corresponding values of the correlation time
    $\tau$ range from 0 to 69. \ref{fig:localization_ratio2}: $\ln
    (f_\M - f)$ is plotted versus $\ln \phi$, where $f$ stands for the
    ratio of localized eigenvectors. The fitted curves are linear.}
\end{figure}

\begin{table}[htb!]
  \centering
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    & $\psi$ & $\sigma$ & $\bar{v}$ & $\mu$ \\
    \hline
    Volvo B & -1.5747e-02 & 4.6929e-01 & -6.2304e+00 &
    -5.3040e-05 \\
    Nordea Bank & 1.7234e-02 & 4.2780e-01 & -6.3758e+00 & 7.5230e-05
    \\
    Ericsson B & 1.8486e-02 & 4.4905e-01 & -6.2834e+00 & -9.2817e-05 \\
    \hline
  \end{tabular}
  \caption{\small \it Parameter Values of Selected Assets'
    returns. The time series are 30-minute returns and run from
    2013/10/10 to 2014/03/12.}
  \label{tab:assets_params}
\end{table}

\begin{table}[htb!]
  \centering
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    & mean & std & skewness & kurtosis \\
    \hline
    \multirow{2}{*}{Volvo B} & -8.6766e-05 & 2.4500e-03 &
    -2.7217e-02 & 7.3394e+00 \\
    & -6.9281e-05 & 2.4538e-03 & -7.2677e-02 & 7.2472e+00 \\
    \hline
    \multirow{2}{*}{Nordea Bank} & 7.4821e-05 & 2.0500e-03 &
    6.9433e-02 & 6.7427e+00 \\
    & 8.8983e-05 & 2.0443e-03 & 6.7125e-02 & 6.2446e+00 \\
    \hline
    \multirow{2}{*}{Ericsson B} & -8.2606e-05 & 2.2939e-03 &
    2.6586e-01 & 7.6716e+00 \\
    & -7.5675e-05 & 2.2844e-03 & 7.8573e-02 & 6.7299e+00 \\
    \hline
  \end{tabular}
  \caption{\small \it Moments of Selected Assets' returns. For each return
    series, the 1st row contains the sample moments, while the 2nd
    constains those computed with MLE parameters. The time series are
    30-minute returns and run from 2013/10/10 to 2014/03/12.}
  \label{tab:assets_moments}
\end{table}

>>>>

\input{summary}
\input{appendix}
